---
title: "afternoon_activity"
author: "Charles Hendrickson"
date: "8/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
```

## Read in data 
```{r}
meteorological_data <- read.csv(here("data", "ntl20_v6.csv"), na = c("NA", -999))

ice_cover_duration <- read.csv(here("data", "ntl33_v7.csv"), na = c("NA", -999))
```

# Create a visualization that compares ice duration across different lakes in the Madison Lake Area. 
```{r}
ggplot(data = ice_cover_duration, aes(x = lakeid, y = ice_duration)) +
  geom_point()

```

# Create an exploratory visualization of mean ice cover duration by year for the Madison Lake Area

```{r}
# Find the mean ice cover duration in Madison Lake Area by year

mean_ice_duration <- ice_cover_duration %>% 
  group_by(year4) %>% 
  summarize(mean_ice = mean(ice_duration))

ggplot(data = mean_ice_duration, aes(x = year4, y = mean_ice)) +
  geom_point() +
  labs(
    x = "Year",
    y = "Mean Ice Duration (days)",
    title = "Mean Ice Duration for Madison Lake Area by Year"
  )


```

### There is a negative linear correlation between `Year` and `Mean Ice Duration` in the Madison Lake Area. 


#
```{r}
mean_air_temp <- meteorological_data %>% 
  group_by(year4, month) %>% 
  summarize(mean_ave_air_temp = mean(ave_air_temp_adjusted)) %>% 
  filter(month %in% c(12, 1, 2))

ggplot(data = mean_air_temp, aes(x = year4, y = mean_ave_air_temp)) +
  geom_point() +
  labs(
    x = "Year",
    y = "Mean Average Air Temperature (Celcius)", 
    title = "Mean Winter Air Temperature for Madison Lake Area"
  )

```

### There is a positive linear correlation between `Year` and `Mean Average Air Temperature` in the Madison Lake Area. 


# Join the mean winter air temperatures to the mean ice cover duration data you found above
```{r}
join_data <- left_join(mean_ice_duration, mean_air_temp)

```

```{r}
ggplot(data = join_data, aes(x = mean_ice, y = mean_ave_air_temp)) +
  geom_point()
```






























